**Operating model**

### 2023-02-14 Rmd/ddMac.Rmd
updates omMac and ddMac

---
title: "**Density Dependence**"
subtitle: "Mackerel: density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

@@

```{r, pkgs}
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(ggplotFL)

@@

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "dd"))

@@

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.2/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.2,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))
```

@@

```{r}
dat=ddWt(stock.wt(eq),biomass(eq),refpts(eq)["msy","biomass"]) 
dat=merge(as.data.frame(dat,drop=T),as.data.frame(biomass(eq)%/%refpts(eq)["msy","biomass"],drop=T),by="year")
names(dat)[3:4]=c("mass","biomass")

@@

```{r, dd-eq-mass}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)=fbar(x)[,1]
fbar(x)[]=c(fbar(eq))*2

@@

ggplot()+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(x, biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T))+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(eq,biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T),col="red")+
  xlab("SSB")+ylab("Catch")
```

@@

```{r, dd-eq-mass-mat}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)[,1]=c(seq(0,max(fbar(eq)),length.out=51),seq(1,50,length.out=51)*max(fbar(eq)))[-52]
fbar(x)=fbar(x)[,1]

@@

```{r, dd-eq-mass-mat-m}
x=propagate(eq,151)
fbar(x)=FLQuant(c(seq(0,max(fbar(eq)),length.out=51),seq(1,100,length.out=101)*max(fbar(eq)))[-152],dimnames=list(iter=seq(151)))

@@

```{r, check1}
f=FLQuant(c(rep(seq(0,1,length.out=51),each=101),rep(seq(1,25,length.out=61)[-1],each=101)),
          dimnames=list(year=dimnames(om)$year,iter=seq(101)))%*%refpts(eq)["msy","harvest"]
fbar(eq)=f

@@

om2=om
for (year in dimnames(om2)$year[-1]){
  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }
catch(om2)=computeCatch(om2,slot="all")
```

```{r, check2}
plot(window(FLStocks("OM"=om,DD=om2),start=40))  
```

@@

```{r}
save(par,file="../data/om/parMac.RData")
```

>>>>

---
title: "**Density Dependence**"
subtitle: "Mackerel: density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
mathjax: TRUE

@@

```{r include=FALSE}
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(ggplotFL)

@@

```{r, dbox}

source("../R/get_dropbox.R")

dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

@@

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.15/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.2,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))

```

```{r}

as.data.frame(par) %>% pander::pandoc.table(style="simple")

```

@@

```{r}

dat=ddWt(stock.wt(eq),biomass(eq),refpts(eq)["msy","biomass"]) 
dat=merge(as.data.frame(dat,drop=T),as.data.frame(biomass(eq)%/%refpts(eq)["msy","biomass"],drop=T),by="year")
names(dat)[3:4]=c("mass","biomass")

@@

```{r, dd-eq-mass}

# Start the clock
ptm <- proc.time()

x=propagate(eq,length(dimnames(eq)$year))
fbar(x)=fbar(x)[,1]
fbar(x)[]=c(fbar(eq))*2

@@

ggplot()+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(x, biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T))+
  geom_line(aes(biomass,catch),
            data=model.frame(FLQuants(eq,biomass=function(x) biomass(x), catch=function(x) catch(x)),drop=T),col="red")+
  xlab("SSB")+ylab("Catch")

# Stop the clock
proc.time() - ptm

```

@@

```{r, dd-eq-mass-mat}

# Start the clock
ptm <- proc.time()

x=propagate(eq,length(dimnames(eq)$year))
fbar(x)[,1]=c(seq(0,max(fbar(eq)),length.out=51),seq(1,50,length.out=51)*max(fbar(eq)))[-52]
fbar(x)=fbar(x)[,1]

@@

```{r, dd-eq-mass-mat-m}

# Start the clock
ptm <- proc.time()

x=propagate(eq,151)
fbar(x)=FLQuant(c(seq(0,max(fbar(eq)),length.out=51),seq(1,100,length.out=101)*max(fbar(eq)))[-152],dimnames=list(iter=seq(151)))

@@

```{r message=FALSE, warning=FALSE}

# Start the clock
ptm <- proc.time()

f=FLQuant(c(rep(seq(0,1,length.out=51),each=101),rep(seq(1,25,length.out=61)[-1],each=101)),
          dimnames=list(year=dimnames(om)$year,iter=seq(101)))%*%refpts(eq)["msy","harvest"]
fbar(eq)=f

@@

om2=om
for (year in dimnames(om2)$year[-1]){
  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }
catch(om2)=computeCatch(om2,slot="all")

# Stop the clock
proc.time() - ptm

```

```{r message=FALSE, warning=FALSE}
plot(window(FLStocks("OM"=om,DD=om2),start=40))  
```

@@

```{r}
save(par,file=file.path(dropboxdir,"data/om/parMac.RData"))

```

### 2023-02-14 Rmd/omMac.Rmd
updates omMac and ddMac

---
title: "**Density Dependence**"
subtitle: "Mackerel: Operating Model with density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
bibliography: refs.bib
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/mac/om/",
               fig.path  ="../tex/figs/mac/om/",
               fig.width =8,
               fig.height=6,
               dev       ="png")

iFig=0
iTab=0
```

```{r, pkgs}
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(ggplotFL)

@@

theme_set(theme_bw(16))
```

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "dd"))

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```

```{r}
source("~/Desktop/projects/ddmse/R/dd.R")
```

```{r}
load(file.path(dropboxdir,"data/om/mac.RData"))
```

```{r, ices}
load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)

@@

dices=model.frame(FLQuants(ices[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                         "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
ggplot(dices)+
  geom_line(aes(SSB,Yield))
```

@@

```{r, vpa}
load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)
vpa =ices+FLAssess:::VPA(ices)

@@

dvpa=model.frame(FLQuants(vpa[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                       "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
pvpa=ggplot(dvpa)+
  geom_line(aes(SSB,Yield))
```

@@

```{r, vpaM}
load("../data/om/parMac.RData")
par["m1"]  =par["m1"]/10
par["w50"] =par["w50"]/1000
par["matk"]=30

@@

d1=model.frame(FLQuants(vpaM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                      "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
d=rbind(cbind("What"="ICES",dices),
        cbind("What"="VPA",dvpa),
        cbind("What"="M",d1))
ggplot(d)+
  geom_line(aes(SSB,Yield,col=What))
```

```{r, vpaDDM}
source("~/Desktop/projects/ddmse/R/dd.R")

@@

ggarrange(p1,p2,p3,p4, ncol=2, nrow=2)
```

```{r, vpaDDMM}
vpaDDMM =vpaM

@@

ggarrange(p1,p2,p3,p4, ncol=2, nrow=2)
```

@@

```{r, vpaDDMMM}
vpaDDMMM=vpaM

>>>>

---
title: "**Operating model**"
subtitle: "Mackerel: Operating Model with density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
mathjax: TRUE

tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
# bibliography: refs.bib
---

```{r warning=FALSE, cache=FALSE, include=FALSE, knitr, eval=TRUE}

knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               cache     =TRUE,
               cache.path="../cache/mac/om/",
               fig.path  ="../tex/figs/mac/om/",
               fig.width =8,
               fig.height=6,
               dev       ="png")

iFig=0
iTab=0

library(FLCore)
library(FLBRP)
library(FLasher)
library(FLife)
library(ggplotFL)

@@

theme_set(theme_bw(16))

source("../R/get_dropbox.R")

dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

if ("try-error"%in% is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}

# source("~/Desktop/projects/ddmse/R/dd.R")
source("../R/dd.R")

```

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}

load(file.path(dropboxdir,"data/om/mac.RData"))

```

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}

# Start the clock
ptm <- proc.time()

load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)

@@

dices=model.frame(FLQuants(ices[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                         "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
ggplot(dices)+
  geom_line(aes(SSB,Yield))

# Stop the clock
proc.time() - ptm

```

@@

```{r, vpa}

# Start the clock
ptm <- proc.time()

load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)
vpa =ices+FLAssess:::VPA(ices)

@@

dvpa=model.frame(FLQuants(vpa[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                       "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
pvpa=ggplot(dvpa)+
  geom_line(aes(SSB,Yield))

# Stop the clock
proc.time() - ptm
```

@@

```{r, vpaM}

# Start the clock
ptm <- proc.time()

load(file.path(dropboxdir, "data/om/parMac.RData"))
par["m1"]  =par["m1"]/10
par["w50"] =par["w50"]/1000
par["matk"]=30

@@

d1=model.frame(FLQuants(vpaM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                      "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
d=rbind(cbind("What"="ICES",dices),
        cbind("What"="VPA",dvpa),
        cbind("What"="M",d1))
ggplot(d)+
  geom_line(aes(SSB,Yield,col=What))

# Stop the clock
proc.time() - ptm
```

\newpage

```{r}

as.data.frame(par) %>% pander::pandoc.table(style="simple")

```

\newpage

```{r, vpaDDM}

# source("~/Desktop/projects/ddmse/R/dd.R")

# Start the clock
ptm <- proc.time()

@@

ggarrange(p1,p2,p3,p4, ncol=2, nrow=2)

# Stop the clock
proc.time() - ptm
```

\newpage

```{r, vpaDDMM}

# Start the clock
ptm <- proc.time()

vpaDDMM =vpaM

@@

ggarrange(p1,p2,p3,p4, ncol=2, nrow=2)

# Stop the clock
proc.time() - ptm
```

@@

\newpage

```{r, vpaDDMMM}

# Start the clock
ptm <- proc.time()

vpaDDMMM=vpaM
